### 2011-04-05 Spatial_adaptation/standing-variation.tex
/* Standing variation */ math oops
/* Standing variation */ added about remaining variance in branching process
/* Standing variation */ entered relations between various quantities (ie how to find proportion of new mutations, etc)

@@

Now, if $f(t) = vt$, then $f^{-1}(r) = r/v$,
and so we have
\[
    \chi = \frac{ v }{ \lambda \chi^d \omega_d } = \left( \frac{ v(1-\lambda_0 \omega_d) }{ \lambda \omega_d } \right)^{1/(d+1)} ,
\]
and 
\[
    \pi_0 = \frac{\lambda_0}{\lambda} v^{d/(d+1)} (1-\lambda_0 \omega_d)^{d/(d+1)} (\lambda \omega_d)^{1/(d+1)} .
\]

>>>>

What about how much variance is left in the branching process?
Well, since $Z_{t+s} = \sum_{k=1}^{Z_t} Z^k_{s}$, where $Z^k_s$ are iid copies of $Z_s$,
we have that $\var[Z_{t+s}|Z_t] = Z_t \var[Z_s]$,
and so the coefficient of variation of $Z_{t+s}$ given $Z_t$ is
\[
   \mathop{CV}[Z_{t+s}|Z_t] &= \frac{\sqrt{Z_t \var[Z_s]}}{ Z_t \E[Z_s] } \\
        &= e^{-rs} \sqrt{ \var[Z_s] } Z^{-1/2} \\
        &\simeq e^{-rt/2} \sqrt{ \var[W] } .
\]

@@

Now, if $f(t) = vt$, then $f^{-1}(r) = r/v$,
and so we have
\[
    \chi = \frac{ v (1-\lambda_0 \omega_d) }{ \lambda \chi^d \omega_d } = \left( \frac{ v(1-\lambda_0 \omega_d) }{ \lambda \omega_d } \right)^{1/(d+1)} ,
\]
and 
\[
    \pi_0 = \frac{\lambda_0}{\lambda} v^{d/(d+1)} (1-\lambda_0 \omega_d)^{d/(d+1)} (\lambda \omega_d)^{1/(d+1)} .
\]

\section{General relationship between various quantities}

We know that there are $\lamba_0$ successful standing variants per unit area;
suppose that there are $\nu_+$ successful new mutants per unit area.
Therefore, $\lambda_0+\nu_+$ is the mean number of successful mutants per unit area (duh),
and $1/(\lambda_0+\nu_+)$ is the mean area associated with a randomly chosen patch.
Let $p_0$ be the proportion of space occupied by standing variants, 
let $a_0$ be the mean area associated with a randomly chosen standing variant,
and let $a_+$ be the mean area associated with a randomly chosen new variant,
so that
\[
    p_0 = \frac{ \lambda_0 a_0 }{ \lambda_0 a_0 + \nu_+ a_+ } = \lambda_0 a_0 ,
\]
since the denominator is equal to 1.

We know how to calculate $p_0$, above, from thinking about the competing exponentials,
which allows us to find $a_0$.

Now, as in the first paper, the mean density of new patches is easy to calculate -- 
$\lambda \nu_+ = \E[\tau]$, where $\tau$ is the mean adaptation time of a point;
this is because 
\begin{align*}
    \P\{ \tau > t \} &= \P\{ \mbox{no points in $t$-cone} \} \\
            &= (1/\lambda) \P\{ \mbox{new successful adaptation arises in non-occupied $(t+dt,x+dx)$} \} ;
\end{align*}
integrating over $t$ produces the result.

Finally, the proportion of patches that come from new mutation is $\nu_+ / (\nu_+ + \lambda_0)$,
and we know that, conditioning on the type of a randomly chosen patch,
\[
    \frac{1}{\lambda_0+\nu_+} = \frac{\lambda_0}{\lambda_0+\nu_+} a_0 + \frac{\nu_+}{\lambda_0+\nu_+} a_+ .
\]
So, given $\lambda_0$, $\nu_+$, and $a_0$, we can find $a_+$.
